%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Beamer Presentation - LaTeX - Template Version 1.0 (10/11/12)
% This template has been downloaded from: http://www.LaTeXTemplates.com
% License: % CC BY-NC-SA 3.0 (http://creativecommons.org/)
% Modified by Rahmat M. Samik-Ibrahim

% REV004 Mon 21 Feb 2022 13:30:00 WIB
% REV003 Mon 14 Feb 2022 21:50:54 WIB
% REV001 Mon 07 Feb 2022 05:54:47 WIB
% STARTX Wed 14 Sep 2016 10:45:19 WIB
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% PACKAGES AND THEMES 
\documentclass[aspectratio=169, xcolor=table, notheorems, hyperref={pdfpagelabels=false}]{beamer}
\input{beamer.tex}
\input{spHH.tex}

% XXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXX
% The short title appears at the bottom of every slide, 
% the full title is only on the title page
% \date{\today}
\title[\kopikopi]
{CSCE604227 System Programming \\
CSCE604227 Pemrograman Sistem \\
Week 02:
Revisit Linux From Scratch}
\author{C. BinKadal}
\institute[SDN]
{
Sendirian Berhad\\
\medskip
\url{https://sp.vlsm.org/Slides/sp02.pdf}
\\ \texttt{Always check for the latest revision!}
}
\date{\revision}

% XXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXX
\begin{document}

\lstset{
basicstyle=\ttfamily\tiny, % \tiny \small \footnotesize 
breakatwhitespace=true,
language=C,
columns=fullflexible,
keepspaces=true,
breaklines=true,
tabsize=3, 
showstringspaces=false,
extendedchars=true}

\section{Start}
\begin{frame}
\titlepage
\end{frame}

% XXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXX

\input{spII-jadwal.tex}

% XXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXX
% Throughout your presentation, if you choose to use \section{} and
% \subsection{} commands, these will automatically be printed on
% this slide as an overview of your presentation
\section{Agenda}
\begin{frame}{Outline}
  \frametitle{Agenda}
  \tableofcontents[sections={1-}]
\end{frame}
% \begin{frame}
%    \frametitle{Agenda (2)}
%    \tableofcontents[sections={12-}]
% \end{frame}

% XXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXX
\section{LFS: Linux From Scratch}
\begin{frame}
\frametitle{LFS: Linux From Scratch}
\begin{itemize}
\item \href{https://youtu.be/jEoM3qan9Gs}{THIS IS HOW WE DOIT!}
\item \url{http://www.linuxfromscratch.org/lfs/view/stable/}
\item To build a GNU/Linux system from scratch (source code).
\item To learn a GNU/Linux system inside out.
\item To use a Virtual Machine.
\item A Chicken and Egg dependency problem:
\begin{itemize}
\item It would be best if you had the tools to build an Operating System.
\item You need an Operating System to build tools.
\item To build a cross-toolchain (compiler and its libraries).
\item To build cross utilities using the cross-toolchain.
\item To build an Operating System in a chroot environment.
\item To do iterations (if necessary).
\end{itemize}
\item How deep would you like to know of a ''real'' Operating System?
\item \textbf{YOU} decide!
\end{itemize}
\end{frame}

% XXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXX
\section{Gnulib --- The GNU Portability Library}
\begin{frame}
\frametitle{Gnulib --- The GNU Portability Library\footnote{%
) Adopted from \url{https://www.gnu.org/software/gnulib/}%
})}

\begin{itemize}
\item a central location for common GNU code
\item intended to be shared among GNU packages at the source level
\item no distribution tarball 
\item See also:
\begin{itemize}
\item GNU Coding Standards --- \url{https://www.gnu.org/prep/standards/}
\item Information for maintainers --- \url{https://www.gnu.org/prep/maintain/}
\item Licenses --- \url{https://www.gnu.org/licenses/}
\item Config --- \url{https://savannah.gnu.org/projects/config/}
\end{itemize}
\end{itemize}

\end{frame}

% XXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXX
\section{Autotools}
\begin{frame}
\frametitle{Autotools\footnote{%
) Adopted from \url{https://www.gnu.org/software/automake/faq/}%
})}

\begin{itemize}
\item Refers to the software packages, consists of programs:
\begin{itemize}
\item Autoconf: helps create portable configure and testsuite scripts.
\begin{itemize}
\item URL: \url{https://www.gnu.org/software/autoconf/}
\item autoreconf
\item autoconf
\item autoheader
\item autoscan
\end{itemize}
\item Automake: helps create portable Makefiles.
\begin{itemize}
\item URL: \url{https://www.gnu.org/software/automake/}
\item aclocal
\item automake
\end{itemize}
\item Libtool: helps create and use shared libraries portably. 
\begin{itemize}
\item URL: \url{https://www.gnu.org/software/libtool/}
\item libtoolize
\end{itemize}
\end{itemize}
\item See also:
\begin{itemize}
\item Autotools Mythbuster --- \url{https://autotools.info/}
\item \href{https://www.gnu.org/savannah-checkouts/gnu/automake/manual/automake.html\#Hello-World}{Small Autotools ''Hello World'' Example}
\end{itemize}
\end{itemize}

\end{frame}

% XXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXX
\section{Small Autotools "Hello World" Example}
\begin{frame}[fragile]
\frametitle{Small Autotools "Hello World" Example (1)\footnote{%
) Adopted from {\tiny \url{https://www.gnu.org/savannah-checkouts/gnu/automake/manual/automake.html\#Hello-World}}%
})}

\begin{itemize}
\item Try this and push it to \url{https://github.com/os2xx/sharesp221/}
\begin{itemize}
\item Work inside your \texttt{autotools/} folder.
\end{itemize}

\item \textbf{Filename:} \texttt{src/main.c}
% \begin{lstlisting}[basicstyle=\ttfamily\tiny]
\begin{lstlisting}[basicstyle=\ttfamily\small]

#include <config.h>
#include <stdio.h>

int
main (void)
{
  puts ("Hello World!");
  puts ("I am cbkadal and this is " PACKAGE_STRING ".");
  return 0;
}

\end{lstlisting}
\end{itemize}

\end{frame}

% XXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXX
\begin{frame}[fragile]
\frametitle{Small Autotools "Hello World" Example (2)}

\begin{itemize}
\item \textbf{Filename:} \texttt{README}
% \begin{lstlisting}[basicstyle=\ttfamily\tiny]
\begin{lstlisting}[basicstyle=\ttfamily\small]
This is a demonstration package for GNU Automake.
Type 'info Automake' to read the Automake manual.
Makefile.am and src/Makefile.am contain Automake instructions 
for these two directories.
\end{lstlisting}

\item \textbf{Filename:} \texttt{src/Makefile.am}
\begin{lstlisting}[basicstyle=\ttfamily\small]
bin_PROGRAMS = hello
hello_SOURCES = main.c
\end{lstlisting}

\item \textbf{Filename:} \texttt{Makefile.am}
\begin{lstlisting}[basicstyle=\ttfamily\small]
SUBDIRS = src
dist_doc_DATA = README

\end{lstlisting}
\end{itemize}

\end{frame}

% XXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXX
\begin{frame}[fragile]
\frametitle{Small Autotools "Hello World" Example (3)}

\begin{itemize}
\item \textbf{Filename:} \texttt{configure.ac}
\begin{lstlisting}[basicstyle=\ttfamily\small]
AC_INIT([amhello], [1.0], [bug-automake@gnu.org])
AM_INIT_AUTOMAKE([-Wall -Werror foreign])
AC_PROG_CC
AC_CONFIG_HEADERS([config.h])
AC_CONFIG_FILES([
   Makefile
   src/Makefile
])
AC_OUTPUT

\end{lstlisting}

\item \textbf{RUN:}
\begin{lstlisting}[basicstyle=\ttfamily\small]
autoreconf --install
./configure
make
src/hello

\end{lstlisting}
\end{itemize}

\end{frame}

% XXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXX
\end{document}

